ShrinkNets

### 2018-01-04 paper/paper.tex

\newcommand{\srm}[1]{\textcolor{red}{{\bf Sam:} #1}}
\begin{document}
\title{ShrinkNets}

@@

\begin{abstract}
  Write the abstract at the end !
\end{abstract}

@@

When designing Neural Networks, finding the appropriate size (width and depth) is key. In particular, these hyper parameters have a strong correlation with over/underfitting \srm{give reference}. The main problem is that we have no reliable way to find them [ref]. Decades of experimentation led to some heuristics [ref] that try to prune that immense space of possible network sizes, but we are still bound to use costly and sometimes complex methods to find reasonable values for these hyper-parameters.

@@

% \subsection{Main Contributions}
% 
% The main contribution of this article are:
% \begin{itemize}
%   \item The Filter layer, a neural network layer which puropose is to allow feature selection
%   \item To the best of our knowledge, the first attempts to dynamically change the number of channels in deep convolutional neural networks
%   \item A deep learning library built on top of PyTorch that allow partictionners to train shrinking networks (Feed-Forward and Convolutional)
% \end{itemize}
% 
\section{Related Work}

\par In the literature we can see different ways of approaching this issue. The first one is to select parameters, train the model, evaluate it, repeat and pick the best one. There are many different ways of selecting parameters: random search [ref], grid search [ref], meta gradient descent [ref], Parsen trees[ref], Gaussian processes [ref] etc... but they all suffer from one major drawback: we have to train and evaluate a very large number of models; and even if some algorithms allow parallel evaluations [ref] to reduce the overall training time, the hardware and energy cost is still very significant.
\par To reduce the number of models trained, another approach is to train a slightly bigger model and after convergence, remove as many parameters as possible without impacting the performance of the model. Notable contributions are Optimal Brain Damage [ref], Deep Compression [ref], and Group sparsity [ref] (this one is especially related to this article). These techniques are very interesting but they still require a reasonable network size to start with, so they usually have to be combined with classic hyper-optimization techniques.
\par However, some recent contributions like Non-Parametric Neural Netowrks [ref] and [ref] try to learn the network size (width for the former and depth for the latter) during the training process and without any prior assumption about the network size.
\srm{Give a short sentence about how our approach is different than these previous approaches.}

\section{The Filter Layer}
\subsection{Motivation}

\srm{This makes what we have done sound like an incremental change over prior work.  Instead, move this description to prior work and say why its not a good approach there, then describe what we do as a new method.  }
The method described in [ref] grows and shrinks the network over time. Though this seems to be an attractive property to have, during our experiments and according to their results, models are very slow to train and sometimes converge to suboptimal solutions. Their method also requires a new optimizer \textit{AdaRad}. Our goal was to provide a solution that can easily be integrated in existing machine learning systems and provide similar convergence speed and accuracy. Therefore, designing a new layer that only allow shrinking seemed to be best approach.
\srm{How is this shrinking approach different than previous approaches like Optimal Brain Damage, Deep Compression,e tc?}

\srm{Describe our key approach at a high level -- i.e., add a new layer to the network, called the {\it filter layer}, which ... }
\subsection{Definition}

In this section we define the \textit{Filter Layer}. It takes an input of size $\left(B \times C \times D_1 \times \dots \times D_n\right)$. So it is compatible with fully connected layers with $n=0$ or convolutional layers with $n=2$. This layer has a parameter $\theta \in \mathbb{R}^C$ and is defined the following way. \srm{Need to define B, C, D}.  
\begin{equation}
  Filter(I;\theta) = I \circ \max(0, \theta)
\end{equation}

Where $\circ$ is the Hadamard product (pointwise multiplication), and $\theta$ is expanded in all dimensions except the second one to match the input size. It is easy to see that if for any $k$, if $\theta_k \leq 0$, the $k^{\text{th}}$ feature/channel will forever be $0$. We can use this property to devise a training procedure.  \srm{Give an English description of what this formalism achieves -- what does the filter layer do, why is it significant.}

\subsection{The training procedure}

To train networks we need start with a substantially oversized network, then we insert \textit{Filter Layers}  (usually after every linear or convolutional layer except the last one) and we sample their weight from the $\text{Uniform}(0, 1)$ distribution. We could train this network directly and it would be equivalent to a normal neural network. However, our goal is to find the smallest network with reasonable performance. We can achieve that by introducing sparsity in the parameters of the \textit{Filter Layers}. Indeed, \srm{having a negative value where?} having a negative value is equivalent to zeroing an entire row and column in the surrounding layers. These disabled neurons/channels can be removed from the network without changing its output (we describe how we perform this removal below). To obtain this sparsity we simply redefine the loss function:

@@

@@

@@

@@

>>>>

\newcommand{\srm}[1]{\textcolor{red}{{\bf Sam:} #1}}
\newcommand{\ra}[1]{\textcolor{blue}{{\bf ra:} #1}}
\begin{document}
\title{ShrinkNets}

@@

%\begin{abstract}
%  Write the abstract at the end !
%\end{abstract}

@@

When designing Neural Networks, finding the appropriate size (width and depth)
is key. In particular, these hyper parameters have a strong correlation with
over/underfitting \srm{give reference}. The main problem is that we have no
reliable way to find them [ref]. Decades of experimentation led to some
heuristics [ref] that try to prune that immense space of possible network sizes.
For example, researchers have used strategies such as random search,
meta-gradient descent and parser trees to reduce find good parameters without
exhaustively exploring the entire hyper-parameter space. Although these
strategies help with finding a good set of hyper-parameters, they still require
a compute-intensive search of the space.

%However, we are still bound to use costly and sometimes complex methods to find
%reasonable values for these hyper-parameters.

@@

In this paper we present a method to automatically find an appropriate network
size without paying the compute and time cost of searching through a large
hyper-parameter space. The key idea is to \emph{learn} the right network size at
the same time that the network is learning the main task. For example, for an
image classification task, with our approach we can provide the training data to
a network---without sizing it a priori---and expect to end up with a network
that has learnt the task without overfitting. This approach has two main
benefits. First, we do no longer need to choose a network size before training.
Second, the final network size will be appropriate for the task at hand, and not
larger. This is important because oversized networks have a lower inference
throughput.

Our approach has two main challenges. First, on how to dynamically size the
network during training. Second, on how to find a loss function that optimizes
for the additional task of sizing, without deteriorating the learning
performance of the main task. We describe next ShrinkNets, which cope with both
challenges:

% \subsection{Main Contributions}
% 
% The main contribution of this article are:
% \begin{itemize}
%   \item The Filter layer, a neural network layer which puropose is to allow feature selection
%   \item To the best of our knowledge, the first attempts to dynamically change the number of channels in deep convolutional neural networks
%   \item A deep learning library built on top of PyTorch that allow partictionners to train shrinking networks (Feed-Forward and Convolutional)
% \end{itemize}
%

\section{ShrinkNets}

\srm{Describe our key approach at a high level -- i.e., add a new layer to the
network, called the {\it filter layer}, which ... }

Our approach consists of starting the training process for the task of interest
with an explicitly oversized network. Then, as training progresses, we learn
which neurons are not contributing to learning the main task and remove them
dynamically, thus shrinking the network size. This method requires two building
blocks. First, a way of identifying neurons that are not contributing to the
learning process, and second a way of balancing the network size and the
generalization capability for the main task. We introduce a new layer, called
\textsf{Filter}, which takes care of \emph{deactivating} neurons. We also modify
existing loss functions to incorporate a new term that takes care of balancing
network sizing and generalization capability appropriately. We explain them
next:

%\subsection{Motivation}
%
%\srm{This makes what we have done sound like an incremental change over prior
%work.  Instead, move this description to prior work and say why its not a good
%approach there, then describe what we do as a new method.  }
%
%The method described in [ref] grows and shrinks the network over time. Though
%this seems to be an attractive property to have, during our experiments and
%according to their results, models are very slow to train and sometimes
%converge to suboptimal solutions. Their method also requires a new optimizer
%\textit{AdaRad}.  Our goal was to provide a solution that can easily be
%integrated in existing machine learning systems and provide similar convergence
%speed and accuracy. Therefore, designing a new layer that only allow shrinking
%seemed to be best approach.
%

%\subsection{Definition}

\textbf{Filter Layer: }

Filter layers have weights in the range $[0,1]$ and are placed after linear and
convolutional layers of traditional deep networks. The \textit{Filter Layer}
takes an input of size $\left(B \times C \times D_1 \times \dots \times
D_n\right)$ so it is compatible with fully connected layers with $n=0$ or
convolutional layers with $n=2$. Their crucial property is a parameter $\theta \in
\mathbb{R}^C$, defined as follows: \srm{Need to define B, C, D}.

\begin{equation} 
Filter(I;\theta) = I \circ \max(0, \theta)
\end{equation}

Where $\circ$ is the Hadamard product (pointwise multiplication), and $\theta$
is expanded in all dimensions except the second one to match the input size. It
is easy to see that if for any $k$, if $\theta_k \leq 0$, the $k^{\text{th}}$
feature/channel will forever be $0$. When this happens, we say the Filter layer
disables the neuron. These disabled neurons/channels can be removed from the
network without changing its output (we describe how we perform this removal
below). We explain next how the weights of the Filter Layer are
adjusted during training.

%We can use this property to devise a training procedure.

\srm{Give an English description of what this formalism
achieves -- what does the filter layer do, why is it significant.}

%To train networks we need start with a substantially oversized network, then we
%insert \textit{Filter Layers}  (usually after every linear or convolutional
%layer except the last one) and we sample their weight from the
%$\text{Uniform}(0, 1)$ distribution.

%The \textit{Filter Layer} takes an input of size $\left(B \times C \times D_1
%\times \dots \times D_n\right)$ so it is compatible with fully connected layers
%with $n=0$ or convolutional layers with $n=2$. This layer has a parameter
%$\theta \in \mathbb{R}^C$ and is defined the following way. \srm{Need to define
%B, C, D}.  
%
%\begin{equation} 
%Filter(I;\theta) = I \circ \max(0, \theta)
%\end{equation}
%
%Where $\circ$ is the Hadamard product (pointwise multiplication), and $\theta$
%is expanded in all dimensions except the second one to match the input size. It
%is easy to see that if for any $k$, if $\theta_k \leq 0$, the $k^{\text{th}}$
%feature/channel will forever be $0$. We can use this property to devise a
%training procedure.  
%
%\srm{Give an English description of what this formalism
%achieves -- what does the filter layer do, why is it significant.}

%\subsection{The training procedure}
\textbf{Training Procedure: } Once Filter layers are placed in a deep network, 
%To train networks we need start with a substantially oversized network, then we
%insert \textit{Filter Layers}  (usually after every linear or convolutional
%layer except the last one) and we sample their weight from the
%$\text{Uniform}(0, 1)$ distribution. 
we could train it directly and it
would be equivalent to a normal neural network. However, our goal is to find the
smallest network with reasonable performance. We achieve that by introducing
sparsity in the parameters of the \textit{Filter Layers}. Indeed, \srm{having a
negative value where?} having a negative value is equivalent to zeroing an
entire row and column in the surrounding layers. To obtain this sparsity, we
simply redefinte the loss function:

@@

Next, we explain how to implement ShrinkNets efficiently.

@@

\ra{this can be shorter. I'd add it as a third paragraph above, immediately
above the eval}

@@

\section{Related Work}

\ra{I'd remove this paragraph because we used it in the motivation already}
\par In the literature we can see different ways of approaching this issue. The
first one is to select parameters, train the model, evaluate it, repeat and pick
the best one. There are many different ways of selecting parameters: random
search [ref], grid search [ref], meta gradient descent [ref], Parsen trees[ref],
Gaussian processes [ref] etc... but they all suffer from one major drawback: we
have to train and evaluate a very large number of models; and even if some
algorithms allow parallel evaluations [ref] to reduce the overall training time,
the hardware and energy cost is still very significant.

\ra{I'd argue these techniques are aimed to improve inference time and not to
avoid hyper-parameter optimization}
\par To reduce the number of models trained, another approach is to train a
slightly bigger model and after convergence, remove as many parameters as
possible without impacting the performance of the model. Notable contributions
are Optimal Brain Damage [ref], Deep Compression [ref], and Group sparsity [ref]
(this one is especially related to this article). These techniques are very
interesting but they still require a reasonable network size to start with, so
they usually have to be combined with classic hyper-optimization techniques.

\srm{How is this shrinking
approach different than previous approaches like Optimal Brain Damage, Deep
Compression,e tc?}

\par However, some recent contributions like Non-Parametric Neural Netowrks
[ref] and [ref] try to learn the network size (width for the former and depth
for the latter) during the training process and without any prior assumption
about the network size. \ra{revise next}This method dynamically grows and shrinks the network
over time. Though this seems to be an attractive property to have, during our
experiments and according to their results, models are very slow to train and
sometimes converge to suboptimal solutions. Their method also requires a new
optimizer \textit{AdaRad}. \ra{explain how difficult is to get the optimizer
stable. that's a drawback of the method} \ra{Instead, ShrinkNets work out of the
box with existing libraries and does not need any changes to the optimizer.}

\srm{Give a short sentence about how our approach is
different than these previous approaches.}

@@

\ra{this can be shorted, and used as conclusions}
